Data Management \\ and LSST Special Programs

### 2022-02-21 ap_docrev.tex
fix typo

In Section 3.6.3.1, ``Absolute Pointing", OSS-REQ-0298\ossreq{0298} specifies that {\it ``the LSST shall point to a defined set of sky coordinates with an RMS accuracy
of" 2 arcseconds ({\tt absPointErr}\reqparam{absPointErr}).

In Section 3.6.3.3, ``Rotator tracking Time, OSS-REQ-0301\ossreq{0301} specifies that {\it ``the LSST shall be able to maintain field rotation tracking over a period of at least"} 1 hour ({\tt rotTrackTime}\reqparam{rotTrackTime}).
The discussion clarifies that this {\it ``is driven by the need to conduct extended 'deep drilling' observations on a single field}.
There do not seem to be any constraints on the speed of the rotator or the minimum distance between successive visits.

>>>>

In Section 3.6.3.1, ``Absolute Pointing", OSS-REQ-0298\ossreq{0298} specifies that {\it ``the LSST shall point to a defined set of sky coordinates with an RMS accuracy
of"} 2 arcseconds ({\tt absPointErr}\reqparam{absPointErr}).

In Section 3.6.3.3, ``Rotator tracking Time, OSS-REQ-0301\ossreq{0301} specifies that {\it ``the LSST shall be able to maintain field rotation tracking over a period of at least"} 1 hour ({\tt rotTrackTime}\reqparam{rotTrackTime}).
The discussion clarifies that this {\it ``is driven by the need to conduct extended 'deep drilling' observations on a single field"}.
There do not seem to be any constraints on the speed of the rotator or the minimum distance between successive visits.
